Associations between chlorophyll *a* and various microcystin-LR health advisory

### 2016-01-25 manuscript/f1000_submission/manuscript.Rmd
fixed table labels

```{r microcystin_levels,echo=FALSE,results='asis'}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_conc_table,format="latex")
print(xtable::xtable(mc_conc_table,
                     label="microcystin_levels",
                     caption="Various suggested microcystin-LR health advisory 
                     concentrations from the USEPA and World Health Organization."), 
      include.rownames=FALSE, comment = FALSE,caption.placement = "top",
      latex.environments = NULL,sanitize.text.function=identity)
```

```{r mc_chla_table, results='asis', echo=FALSE}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_chla_tbl,format="latex")
print(xtable::xtable(mc_chla_tbl,
                     label="mc_chla_table",
                     caption="Chlorophyll \\textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r child_conmat_table, results='asis', echo=FALSE}
#knitr::kable(child_conmat,format="latex")
print(xtable::xtable(child_conmat,
                     label="child_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r who_drink_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_drink_conmat,format="latex")
print(xtable::xtable(who_drink_conmat,
                     label="who_drink_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r adult_conmat_table, results='asis', echo=FALSE}
#knitr::kable(adult_conmat,format="latex")
print(xtable::xtable(adult_conmat,
                     label="adult_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r who_rec_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_rec_conmat,format="latex")
print(xtable::xtable(who_rec_conmat,
                     label="who_rec_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

>>>>

```{r microcystin_levels,echo=FALSE,results='asis'}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_conc_table,format="latex")
print(xtable::xtable(mc_conc_table,
                     label="tab:microcystin_levels",
                     caption="Various suggested microcystin-LR health advisory 
                     concentrations from the USEPA and World Health Organization."), 
      include.rownames=FALSE, comment = FALSE,caption.placement = "top",
      latex.environments = NULL,sanitize.text.function=identity)
```

```{r mc_chla_table, results='asis', echo=FALSE}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_chla_tbl,format="latex")
print(xtable::xtable(mc_chla_tbl,
                     label="tab:mc_chla_table",
                     caption="Chlorophyll \\textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r child_conmat_table, results='asis', echo=FALSE}
#knitr::kable(child_conmat,format="latex")
print(xtable::xtable(child_conmat,
                     label="tab:child_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r who_drink_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_drink_conmat,format="latex")
print(xtable::xtable(who_drink_conmat,
                     label="tab:who_drink_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r adult_conmat_table, results='asis', echo=FALSE}
#knitr::kable(adult_conmat,format="latex")
print(xtable::xtable(adult_conmat,
                     label="tab:adult_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r who_rec_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_rec_conmat,format="latex")
print(xtable::xtable(who_rec_conmat,
                     label="tab:who_rec_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```
